Domain-Driven Code Transformation\\for Solving Partial Differential Equations

### 2014-02-13 paper/bare_conf.tex
Add compiler algorithms

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
% There is also a support site at:
% http://algorithms.berlios.de/index.html
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/

@@

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{A Model-Driven Optimization Approach\\to Solving Partial Differential Equations}

@@

\section{A Model-driven Approach to Code Optimization}
%All the work done in the polyhedral model should be useful, but our kernels fit L1, so they need special attention for what concerns key aspects like managing registers, exploiting ILP in its various forms, and reducing loop overhead. 
%Follows a description of code transformations using our compiler-driven approach.

@@

>>>>

% *** SPECIALIZED LIST PACKAGES ***
%
\usepackage[longend,linesnumbered]{algorithm2e}
\usepackage{algorithmic}

\newcommand{\code}[1]{\lstset{basicstyle=\small\tt}\lstinline£#1£\lstset
{basicstyle=\footnotesize\tt}}

% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
% There is also a support site at:
% http://algorithms.berlios.de/index.html
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/

@@

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Domain-Driven Code Transformation\\for Solving Partial Differential Equations}

@@

\section{A Domain-Driven Approach to Code Optimization}
%All the work done in the polyhedral model should be useful, but our kernels fit L1, so they need special attention for what concerns key aspects like managing registers, exploiting ILP in its various forms, and reducing loop overhead. 
%Follows a description of code transformations using our compiler-driven approach.

\clearpage

@@

The compiler structure

\begin{algorithm}[h]
\caption{The PyOP2 compiler.}
\label{algo:PyOP2Compiler}
  \textbf{The PyOP2 Compiler}\\
  \KwIn{ast, wrapper, isa}
  \KwOut{code}
// Analyze ast and build optimization plan \\
it\_space = analyze(ast) \\
\If{\KwSty{not} it\_space}{
  ast.apply\_inter\_kernel\_vectorization(wrapper)
  \Return{ast.from\_ast\_to\_c()}
}
plan = cost\_model(it\_space.n\_inner\_arrays, isa.n\_regs) \\
~~\\
// Optimize ast based on plan \\
ast.apply\_licm() \\
\If{plan.sz\_split}{
  ast.split(plan.sz\_split)
}
\If{plan.uaj\_factor}{
  ast.vr\_tile(plan.uaj\_factor)
}
ast.padding() \\
ast.data\_align() \\
\Return{ast.from\_ast\_to\_c()}
\end{algorithm}

The compiler cost model. Used to find out tile size and split size.

\begin{algorithm}[h]
\caption{Procedure to estimate the most suitable unroll-and-jam factor and/or split size.}
\label{algo:applyCostModel}
  \textbf{Algorithm: ApplyCostModel}\\
  \KwIn{n\_inner\_arrays, n\_regs}
  \KwOut{uaj\_factor, sz\_split}

%// roundup(A, B) is a function that rounds A up to the nearest multiple of B \\

sz\_split = 0 \\
// Compute spltting factor \\
\While{n\_inner\_arrays $>$ n\_regs}{
  n\_inner\_arrays = n\_inner\_arrays / 2 \\
  sz\_split = sz\_split + 1 
}

n\_inner\_regs = n\_regs / 2 \\
\If{n\_inner\_arrays $>$ n\_inner\_regs \KwSty{or} sz\_split $>$ 0}{
  // Rely on autovectorization, as there might be not enough registers to improve performance by tiling \\
  \Return{$<$sz\_split, 0$>$}
}

// Compute unroll-and-jam factor for vector-register tiling \\
n\_regs\_avail = n\_regs - n\_inner\_arrays \\
uaj\_factor = $\lceil$n\_reg\_avail / n\_inner\_arrays$\rceil$ \\
\Return{$<$sz\_split, uaj\_factor$>$}
\end{algorithm}

\clearpage
